Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-10-31 VMCAI-revised-version/final.tex
effectivity

\begin{proposition}\label{indec WSTS with dcs}
{\sc Resilience} is undecidable for reset-VASS, hence it is also undecidable for $\pred$-basis-effective $\omega^2$-WSTS with strong compatibility and with 
$\Safe=\mathop{\downarrow} \Safe$.
\end{proposition}

>>>>

\begin{proposition}\label{indec WSTS with dcs}
{\sc Resilience} is undecidable for reset-VASS, hence it is also undecidable for $\post$-effective and $\pred$-basis-effective $\omega^2$-WSTS with strong compatibility and with 
$\Safe=\mathop{\downarrow} \Safe$.
\end{proposition}
